# Reproducible Research Peer Assginment 1
========================================================

## Loading Foot Step Activity Data

```{r}
activityDF<-read.csv("activity.csv")
summary(activityDF)
```
##
Compute steps per day
```{r}
totalstepsperdayDF<-aggregate(activityDF$steps ~ activityDF$date, data = activityDF, sum,na.rm = TRUE)
```


## Histogram
```{r}
hist(totalstepsperdayDF[,2],xlab='Total Steps per day',ylab='Number of days',main="Histogram of number of steps each day")

```

## Mean and Median total number of steps taken per day
```{r,echo=FALSE}
mean_totalstepsperdayDF<-as.numeric(mean(totalstepsperdayDF[,2]))
median_totalstepsperdayDF<-median(totalstepsperdayDF[,2])
```
Mean = `r mean_totalstepsperdayDF`
Median = `r median_totalstepsperdayDF`


## Average daily activity pattern
```{r}
averagestepsperintervalDF<-aggregate(activityDF$steps ~ activityDF$interval, data = activityDF, mean,na.rm = TRUE)
plot( averagestepsperintervalDF[,1], averagestepsperintervalDF[,2],ylim=c(0,500),ylab="Average Steps", xlab="Intervals" ,type="l") 
```

```{r,echo=FALSE}
intervalwithmaxsteps<-averagestepsperintervalDF[which.max(averagestepsperintervalDF[,2]),][1]

```

Interval with Max Average steps = `r intervalwithmaxsteps`


## Imputing missing values

```{r,echo=FALSE}
activityNADF<-subset(activityDF,is.na(activityDF$steps))
noofrowswithNAs<-nrow(activityNADF)
```

Total number of missing values in the dataset = `r noofrowswithNAs`


## Filling in all of the missing values in the dataset with mean interval steps

```{r}
colnames(averagestepsperintervalDF)[1] <- "interval"
colnames(averagestepsperintervalDF)[2] <- "avg_steps"

for(i in 1:nrow(activityDF)) {
  
    if(is.na(activityDF[i,]$steps)){
      
      activityDF[i,]$steps<-averagestepsperintervalDF[averagestepsperintervalDF$interval==activityDF[i,]$interval,2]
     
    }
}

```

### Histogram after refilling NA's


Compute steps per day
```{r}
totalstepsperdayDF<-aggregate(activityDF$steps ~ activityDF$date, data = activityDF, sum,na.rm = TRUE)
```

New Historgram after refilling NA's

```{r}
hist(totalstepsperdayDF[,2],xlab='Total Steps per day',ylab='Number of days',main="Histogram of number of steps each day")

```


New Mean and Median total number of steps taken per day after refilling NA's

```{r,echo=FALSE}
mean_totalstepsperdayDF<-as.numeric(mean(totalstepsperdayDF[,2]))
median_totalstepsperdayDF<-median(totalstepsperdayDF[,2])
```
Mean = `r mean_totalstepsperdayDF`
Median = `r median_totalstepsperdayDF`


## differences in activity patterns between weekdays and weekends

